\PaperTitle

### 2024-05-05 Final_Report/paper.tex
Fixed intro errors

  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and LinkedIn. These sets were then merged into a single dataset, which was then split into training and testing sets. 
  Four models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.

  A thorough evaluation of the models was conducted through testing and validation sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  achieved the highest accuracy of $85\%$ and Macro F1 score of 84\%.

>>>>

  For this project, many sets of packet data were collected from three popular websites: ChatGPT, Blackboard, and LinkedIn. These sets were then merged into a single dataset, which was then split into training and validating sets. 
  Four models were then trained and tested on this data: Logistic Regression, K-Nearest Neighbors, Random Forest, and Neural Network \cite{scikit-learn}.

  A thorough evaluation of the models was conducted through test sets, hyperparameter optimization employing cross-validation and grid search, and computing accuracy and Macro F1 scores. The results showed that the Neural Network model 
  achieved the highest accuracy of $85\%$ and Macro F1 score of 84\%.
